Finding Maximum $k$-Cliques Faster Using Lazy Global Domination

### 2016-05-17 paper/paper.tex
No manual figure spacing
AAAI style caps Using

% \frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Finding Maximum $k$-Cliques Faster using Lazy Global Domination)
/Author (Ciaran McCreesh, Patrick Prosser)}
\setcounter{secnumdepth}{0}

\begin{document}
\title{Finding Maximum $k$-Cliques Faster using Lazy Global Domination}
 \author{
    Ciaran McCreesh%
    \thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/K503058/1]}
    \and
    Patrick Prosser
    \\ University of Glasgow, Glasgow, Scotland
}
\maketitle

@@

\begin{figure}[t]
    \centering
    \input{gen-graph-omega}
    \caption{Values of $\tilde{\omega}_k$ for random graphs $G(200, p)$, with varying edge probabilities.
        We see that even for very low edge probabilities, a maximum $k$-clique
    quickly covers the entire graph when $k > 1$.}
    \label{figure:graph-omega}

    \vspace*{2em}
    \centering
    \input{gen-graph-nodes}
    \caption{Search space size for random graphs $G(200, p)^k$, with varying edge probabilities. We see that
        $4$-clique is easier than $3$-clique in practice, which in turn is easier than $2$-clique. (The
        complexity peak for maximum clique occurs at around edge probability 0.9, and requires
        approximately 15 million search nodes.)}
    \label{figure:graph-nodes}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \input{gen-graph-omega-2}
    \caption{The size of a maximum $2$-clique in random graphs $G(n, p)$ with varying edge
        probabilities, and different values of $n$. For $G(50, p)$, a $2$-clique has size average 50
    from $p = 0.42$ onwards.}
    \label{figure:graph-omega-2}

    \vspace*{2em}
    \centering
    \input{gen-graph-nodes-2}
    \caption{The search space size for the maximum $2$-clique problem in random graphs $G(n, p)$
        with varying edge probabilities, and for different values of $n$. As $n$ increases, the
    complexity peak grows and moves slowly to the left.}
    \label{figure:graph-nodes-2}
\end{figure}

>>>>

% \frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Finding Maximum $k$-Cliques Faster Using Lazy Global Domination)
/Author (Ciaran McCreesh, Patrick Prosser)}
\setcounter{secnumdepth}{0}

\begin{document}
\title{Finding Maximum $k$-Cliques Faster Using Lazy Global Domination}
 \author{
    Ciaran McCreesh%
    \thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/K503058/1]}
    \and
    Patrick Prosser
    \\ University of Glasgow, Glasgow, Scotland
}
\maketitle

@@

\begin{figure}[t]
    \centering
    \input{gen-graph-omega}
    \caption{Values of $\tilde{\omega}_k$ for random graphs $G(200, p)$, with varying edge probabilities.
        We see that even for very low edge probabilities, a maximum $k$-clique
    quickly covers the entire graph when $k > 1$.}
    \label{figure:graph-omega}
\end{figure}

\begin{figure}[t]
    \centering
    \input{gen-graph-nodes}
    \caption{Search space size for random graphs $G(200, p)^k$, with varying edge probabilities. We see that
        $4$-clique is easier than $3$-clique in practice, which in turn is easier than $2$-clique. (The
        complexity peak for maximum clique occurs at around edge probability 0.9, and requires
        approximately 15 million search nodes.)}
    \label{figure:graph-nodes}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \input{gen-graph-omega-2}
    \caption{The size of a maximum $2$-clique in random graphs $G(n, p)$ with varying edge
        probabilities, and different values of $n$. For $G(50, p)$, a $2$-clique has size average 50
    from $p = 0.42$ onwards.}
    \label{figure:graph-omega-2}
\end{figure}

\begin{figure}[t]
    \centering
    \input{gen-graph-nodes-2}
    \caption{The search space size for the maximum $2$-clique problem in random graphs $G(n, p)$
        with varying edge probabilities, and for different values of $n$. As $n$ increases, the
    complexity peak grows and moves slowly to the left.}
    \label{figure:graph-nodes-2}
\end{figure}
